Variation in distance between consecutive animal locations

### 2021-03-29 distributions_paper/rudolph_distributions.Rmd
Paragraph of methods

Random walks used broadly in biology to characterize animal and cell movement. Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions. [@codling2008random]
- IDEA: so maybe use these distributions for the angles. We might see that there is not much difference in angle movement across individuals? They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances. 
- Also might be intriguing to incorporate the time as a set of multiple random walks? or repeats the velocity value for that number of minutes. Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$). Hence, turning events occur as a Poisson process with rate $\lambda$. **This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose. So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data.

@@

# Methods
Describe the data collection from the animov outline. 
Add a section that describes the limitations for this telemetry data. 
From book chapter: Attached radio-transmitters at the base of the central tail feathers. Toucan locations measured by triangulation using receivers and hand-held two-element Yagi antennas. 
Tracking periods laster 4-5 hours with individual birds located every 15 minutes. The 15 minute interval to ensure locations within the time frame of seed passage or regurgitation, which are expected to be longer than 15 minutes.

@@

From each of the locations for the twelve individuals, we calculated turning angles (in radians) between subsequent directions, and the associated Euclidean step lengths in meters.

>>>>

Random walks used broadly in biology to characterize animal and cell movement. Describes que commonly used distributions for angles: von Mises, wrapped normal and wrapped Cauchy distributions. [@codling2008random]
- IDEA: so maybe use these distributions for the angles. We might see that there is not much difference in angle movement across individuals? They all tend to move forward perhaps, or something like that, and where the real differences are is in the distances. 
- Also might be intriguing to incorporate the time as a set of multiple random walks? or repeats the velocity value for that number of minutes. Maybe just using a correlated random walk, which takes into account short-term correlations in the direction of movement?
  - Codling describes this as a velocity jump process, since the markov process is the walker's velocity rather than the location. Details at the end of page 7. 
  - We consider the individuals moving in space at a constant speed $\nu$, and at each time step $\tau$ each individual changes direction and moves a distance $\delta$ in a new direction (with probability $r=\lambda\tau$), or moves a distance $\delta$ in the previous direction (with probability $q=1-\lambda\tau$). Hence, turning events occur as a Poisson process with rate $\lambda$. **This is textual from paper, so modify** Their focus is also on multiple individuals at the same time, and the density of individuals at a given time and location.
    - In my case, the distance $\delta$ would also be randomly sampled, or this are the velocities I suppose. So, perhaps it is constant speed, and the distance is actually times to account for 15, 30, etc minutes based on the data. 
    - Remember too that this velocity $\nu$ is actually the distance over time $\delta/\tau$

@@

# Methods

We focused our study of individual variation on the many-banded araçari (*Pterglossus pluricinctus*), a small toucan in Yasuní National Park, Ecuador. Previous studies used radiotelemetry to estimate home ranges and evaluate the potential seed dispersal distances for the *Virola flexuosa* tree [@holbrook2011home, holbrook2007usin]. Over a period of four years, from 2001 to 2005, *P. pluricinctus* individuals were captured and radio-transmitters were attached at the base of the central trail feathers [@holbrook2011home]. Toucan locations were estimated by triangulation using receivers and hand-held antennas, with tracking periods lasting between 4-5 hours per day, locating individual birds every 15 minutes. It is important to note that these methods did not tack all birds simultaneously, and that although individual toucan locations were attempted every 15 minutes, this was not always possible, thus some successive locations have time categories associated to multiples of 15. For our analyses, we focused on toucans with a minimum of **20?** recorded locations, and for each subsequent set of locations we calculated turning angles (in radians), and the associated Euclidean step lengths in meters. We worked under a velocity-based framework, and thus divided step lengths by the time interval during which they were recorded. This gave us a total of **600ish?** data points for angles and velocities.

Describe the data collection from the animov outline. 
Add a section that describes the limitations for this telemetry data. 
From book chapter: Attached radio-transmitters at the base of the central tail feathers. Toucan locations measured by triangulation using receivers and hand-held two-element Yagi antennas. 
Tracking periods laster 4-5 hours with individual birds located every 15 minutes. The 15 minute interval to ensure locations within the time frame of seed passage or regurgitation, which are expected to be longer than 15 minutes.

@@
